---
title: "Kab 8"
author: "Shayan Kaveh"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
library(janitor)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv(here("slo_homes.csv")) %>% 
  clean_names()
```

### Create a subset with 4 cities

Task: create a subset called homes_subset that only contains observations where the city is: - "San Luis Obispo" - Atascadero - Arroyo Grande - Santa Maria-Orcutt

**Use the `%in%` operator or else it will only include values that go in that specific order!!**

```{r}
homes_subset <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt")) # MAKE SURE TO USE %in% IN THIS CASE OR ELSE IT WILL ONLY INCLUDE VALUES THAT GO IN THE SPECIFIC ORDER OF THE PROVIDED VECTOR!!!
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r}
homes_subset %>% 
  group_by(city, status) %>% 
  summarize(mean_price = mean(price),
            sd_price = sd(price))

# not creating a new subset data frame because this is just exploratory
```

Task: explore the relationship betwen sq footage and home price (from home_subset) in a scatterplot.

```{r}
ggplot(data = homes_subset,
       aes(x = sq_ft, y = price)) +
  geom_point(aes(color = city)) +
  geom_smooth(method = "lm") # have to add (`method = "lm"`) to make it a linear model

# follows a linear relationship with a positive correlation between square footage and home price
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price.

Create 2 different permutations of this model:

(1) price ~ city, bedrooms, bathrooms, sq_ft, status (lm1)
(2) price ~ city, sq_ft, status (lm2)
(3) price ~ bedrooms, bathrooms, status (lm3)

```{r}
lm1 <- lm(price ~ city + bedrooms + bathrooms + sq_ft + status, data = homes_subset)

lm2 <- lm(price ~ city + sq_ft + status, data = homes_subset)

lm3 <- lm(price ~ bedrooms + bathrooms + status, data = homes_subset)

# If I wanted SLO to be the reference level:
# Use fct_relevel to specify a new reference level

new_homes_subset <- homes_subset %>% 
  mutate(city = fct_relevel(city, "San Luis Obispo"))

levels(new_homes_subset$city)

# because this is below the `lm`s, it won't affect those models but if I were to redo it, now SLO would be the reference level:

lm_slo <- lm(price ~ city + sq_ft, data = new_homes_subset)
```

adjusted R-squared: explains strength of relationship in difference of variance of home price based on this model


### Explore correlations between quantitative variables

Task: make a subset called homes_qant (starting from homes_subset) that only contains the variable from price through sq_ft

```{r}
homes_quant <- homes_subset %>% 
  select(price:sq_ft)

homes_cor <- cor(homes_quant)

corrplot(homes_cor, method = "ellipse")
```
### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)

# This tells us that model 1 is actually better even though some aspects don't make as much sense
```

### Use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Check out diagnostic plots for lm1

```{r}
plot(lm1)
```

### Use broom::augment() to return the predictions for existing observations

```{r}
home_predictions <- augment(lm1)

# Make a histogram of the residuals from this model (lm1)

ggplot(data = home_predictions,
       aes(x = .resid)) +
  geom_histogram(bins = 50)
```

ok um hi smelly look at us stinking up a new branch
