---
title: "Kab 8"
author: "Shayan Kaveh"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
library(janitor)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv(here("slo_homes.csv")) %>% 
  clean_names()
```

### Create a subset with 4 cities

Task: create a subset called homes_subset that only contains observations where the city is: - "San Luis Obispo" - Atascadero - Arroyo Grande - Santa Maria-Orcutt

**Use the `%in%` operator or else it will only include values that go in that specific order!!**

```{r}
homes_subset <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt")) # MAKE SURE TO USE %in% IN THIS CASE OR ELSE IT WILL ONLY INCLUDE VALUES THAT GO IN THE SPECIFIC ORDER OF THE PROVIDED VECTOR!!!
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r, include = TRUE, eval = FALSE}
homes_subset %>% 
  group_by(city, status) %>% 
  summarize(mean_price = mean(price),
            sd_price = sd(price))
```

